Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-30 draft/paper1_jenny.tex
Edit final sample

    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
    \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
    completeness of our HSC samples.

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
    We compute \mstar{} values for these galaxies using our fiducial 
    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
    Figure~\ref{fig:mass_complete} compares the SMFs of galaxies from 
    \texttt{S82-MGC} with the SMFs of galaxies from our 
    sample\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive galaxies is 
    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
    %The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.    
    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
    where our two samples are complete. 
    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    %Please see the next section and Appendix~\ref{app:match} for more details.

	\jenny{Anything else we need to keep from here?}
	By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z{\sim} 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
%% ------------------------------------------------------------------------------------ %%

@@

	With stellar masses in hand, we now use the redMapper cluster catalog to identify a sample of 
    central galaxies.

	\subsection{Indentifying central galaxies using the \redm{}{} cluster catalog}
    \label{ssec:redmapper}

    We wish to focus on galaxies located at the center of their dark matter halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.

    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    The \redm{} catalog therefore helps us group massive central galaxies into 
    samples with different average \mhalo{}. 
    We will use the central galaxies of \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
    live in massive halos as described below. In addition to identifying central galaxies, 
    we are also able to link each galaxy with a halo mass using the redMaPPer catalog, and 
    this information is also very useful in studying the 
    relationship between galaxy structure and environment.
%% ------------------------------------------------------------------------------------ %%

@@

    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
    To ensure a clean separation in \mhalo{}, here we only focus on the central 
    galaxies of clusters with $\lambda > 30$. 
    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
    We have checked that none of the results in this work depend on the choice of this 
    $\lambda$ limit.

    We therefore match the \texttt{hscZ} sample with the central galaxies of \redm{} clusters 
    with $\lambda \geq 30$ and $P_{\mathrm{0.7}} \geq 0.7$, and find 164 matched 
    galaxies at $0.3 \leq z \leq 0.5$.
    Our sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
    ${\sim} 41$, corresponding to halo mass of 
    $M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
    Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
    ($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
    Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    Out next goal is to construct a sample of central galaxies living in halos with 
    \logmh{}$<14.0$. 
    We first identify and remove all galaxies within a cylindrical region around all 
    \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the uncertainty of the photometric redshift error. 
    We convert $\lambda$ to $M_{\mathrm{halo}}$ using the calibration of 
    \citet{Simet2016} and we use the mass-concentration relation from 
    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. At $0.3 < z < 0.5$, the 
    uncertainty of photo-$z$ is between 0.015 to 0.025, and is enough to exclude 
    cluster members.
    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$\leq 14.0$. 
    We will refer to this sample of \textbf{central galaxies in less massive halos}
    as the \nbcg{} sample. For massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
    At this very high mass end, and given that we have rejected satellites in \redm{} 
    clusters, any further satellite contamination can be safely neglected 
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}).
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
    % TODO: The actual number waits to be updated}

>>>>

    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
    \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
    \citealt{Lawrence2007}). 
    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample 
    complete to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate 
    the completeness of our HSC sample.   
	By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample, which is the main contributor of 
    spec-$z$ in our massive galaxy sample, is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    As the secondary contributor, the GAMA survey is 80\% complete down to 
    $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
    their Fig~~6).

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
    We estimate \mcmodel{} values of these galaxies using our fiducial 
    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
    Figure~\ref{fig:mass_complete} compares the volume number density distributions 
    of galaxies from \texttt{S82-MGC} with the one for galaxies in our 
    sample\footnote{Since we do not apply any statistical correction on the 
    completeness, we do not use the term ``stellar mass function'' to avoid confusion;
    Errors on the distributions are estimated via bootstrap resampling}. 
    Based on Fig~\ref{fig:mass_complete}, we conclude that our sample of massive 
    galaxies is reasonably complete down to \logmcmodel{}${\sim} 11.5$ at 
    $0.3 \leq z \leq 0.5$. 
    %The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.    
    Given the average difference between \mtot{} and \mcmodel{}, we will focus on 
    the galaxies with \logmtot{}$> 11.6$ where our sample shows good completeness.
    The massive galaxies with $11.4 \le$\logmtot{}$<11.6$ are also included in the 
    discussion since there is no obvious reason to worry about the impact of
    completeness on the main results of this work.

    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    %Please see the next section and Appendix~\ref{app:match} for more details.

@@

	With the different estimates of \mstar{} and the \mden{} profiles in hand, we now 
	proceed to identify a sample of massive central galaxies with the help from the 
	\redm{} galaxy cluster catalog. 
	The ``central'' galaxy can be roughly defined as the galaxy that live in the 
	center of its own dark matter halo.  
	In contrast, galaxy in a sub-halo who is orbiting within the virial radius of a 
	more massive halo is referred to as ``satellite''. 
	Central galaxy has its unique importance in the study of galaxy evolution and 
	galaxy-halo coevolution.
	Therefore, to better understand the connection between the structure of massive 
	galaxies and the assembly history of stars and halos, we wish to focus on central 
	galaxies in this work.

\subsection{Candidates of massive central galaxies}
    \label{ssec:redmapper}

    Identification of central galaxy is not an easy task (e.g. \citealt{Yang2007}).
    For this purpose, we first use the \redm{} catalog to help us isolate the central 
    galaxies in massive halos and also exclude the massive satellite galaxies in these
    haloes.  
    Assuming the completeness of the \redm{} catalog, we treat the rest of sample as 
    galaxies from less massive halos.  
    Given the smaller fraction of satellite galaxies at high-\mstar{} end (e.g. 
    \citealt{Reid2014, Hoshino2015, Saito2016}), 
    we further assume that the massive ones (\logmtot{}$>11.4$) among them are likely 
    to be the central galaxies of these smaller halos.

    In the first step, we make use of the \texttt{v5.10} of the \redm{} cluster 
    \footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.

    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    Therefore the central galaxies of these \redm{} clusters\footnote{We only use the 
    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
    galaxies that live in massive halos as described above.
    Besides the selection of central galaxies, we are also able to link each galaxy
    with a \mhalo{} using the \redm{} catalog. 
    Such information is also very useful in studying the relationship between galaxy
    structure and environment (Huang\etal in prep.).
%% ------------------------------------------------------------------------------------ %%

@@

    % TODO: Move this to Paper II
    %To ensure a clean separation in \mhalo{}, here we only focus on the central 
    %galaxies of clusters with $\lambda > 30$. 
    %According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
    %$M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
    %We have checked that none of the results in this work depend on the choice of this 
    %$\lambda$ limit.

    %The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
    %${\sim} 41$, corresponding to halo mass of 
    %$M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
    %Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
    %($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
    %Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.

    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
    clusters with $\lambda \geq 20$ and $P_{\mathrm{0.7}} \geq 0.7$, we find 164 
    matched galaxies at $0.3 \leq z \leq 0.5$.
    This sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$, but the main results 
    of this work are not affected by this.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    As the next step, we want to construct a sample of central galaxies living in halos 
    with \logmh{}$<14.0$. 
    To achieve this, we identify and remove all galaxies within a cylindrical region 
    around all \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the uncertainty of the photometric redshift error of the cluster. 
    We convert $\lambda$ of each cluster to $M_{\mathrm{halo}}$ using the calibration 
    of \citet{Simet2016} and we use the mass-concentration relation from 
    \citet{Diemer2015} to compute $R_{\mathrm{200b}}$. 
    At $0.3 < z < 0.5$, the uncertainty of photo-$z$ is between 0.015 to 0.025, and 
    is enough to exclude cluster members.

    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$< 14.0$. 
    We will refer to this sample of \textbf{potential central galaxies in less 
    massive halos} as the \nbcg{} sample. 
    Since we have rejected satellites in \redm{} cluster and the satellite 
    contamination steadily decreases with stellar mass (e.g. \citealt{Reid2014, 
    Hoshino2015, Saito2016, vanUitert2016}), the massive galaxies in the \nbcg{} 
    sample are very likely to be the central galaxies of

     very high mass end, and given that we have rejected satellites in \redm{} 
    clusters, any further satellite contamination can be neglected for the purpose of 
    this work
    .
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
%% ------------------------------------------------------------------------------------ %%
